Interactive Visualization of Hierarchically Structured Data

### 2017-02-15 treelapse.Rmd
Mention the github
Use png instead of pdf images

We have implemented our visualizations in D3, but encapsulated in an R
package, called treelapse, to facilitate rapid turnover from data
preparation and modeling to interactive exploration, and vice
versa. We hope this package encourages data analysts to work at the
border between data modeling and visualization, and more generally
empowers a wider audience to apply less widely known, but powerful,
visualization ideas.

@@

```{r antibioticoverview, fig.cap = "The two antibiotic time courses are readily apparent even when only highlighting the most abundant taxa."}
include_graphics("figure/antibiotic_overview.pdf")
```

```{r antibioticbacteroidetes, fig.cap = "Introducing a second box into the timebox display identifies the Bacteroidaceae as a taxon only midly impacted by antibiotics."}
include_graphics("figure/antibiotic_bacteroidetes.pdf")
```

@@

```{r ruminococcus, fig.cap = "By hovering over the Ruminoccocus branches, we see that there is a prolonged effect of the antibiotics time courses more or less uniformly across the lower taxonomic orders."}
include_graphics("figure/ruminococcus.pdf")
```

@@

```{r verrucomicrobiae, fig.cap = "The subtree averages aggregation brings attention to the Verrucomicrobiae, which though only present as a few species, are each rather abundant. In particular, they seem to increase after the first antibiotic time course."}
include_graphics("figure/verrucomicrobiae.pdf")
```

@@

```{r pretermcsts, fig.cap = "The increased diversity among samples in CST 4 is represented by the relatively larger contribution of red edges to branches outside of the Firmicutes."}
include_graphics("figure/preterm_csts.pdf")
```

```{r pretermcstslacto, fig.cap = "Zooming into the Lactobacillaceae family, we notice that the difference between the remaining four CSTs is related to which types of Lactobacillus are most prominent."}
include_graphics("figure/preterm_csts_lacto.pdf")
```

```{r pretermpreterm, fig.cap = "Samples with high levels of phyla other than Firmicutes appear to be related to preterm births."}
include_graphics("figure/preterm_preterm.pdf")
```

@@

```{r zillowcities, fig.cap = "California home prices at the city level, between 1996 and 2016. The effect of the 2008 recession is clear, and we have hovered over the San Bernardino series, to display the identity of one of the cities most strongly affected by the recession."}
include_graphics("figure/zillow_cities.pdf")
```

```{r zillowmiddlepre, fig.cap = "Neighborhoods with mid-range home prices before the recession are selected here. Note that the collection of series seems to widen after 2008 -- we are interested in whether there are reliable predictors of these alternate trajectories, given their similar starting points."}
include_graphics("figure/zillow_middle_pre.pdf")
```

```{r zillowmiddleup, fig.cap = "Among those neighborhoods with mid-range prices before the recession, we have selected those that recovered more rapidly. These appear to be located mainly in Los Angeles and San Diego counties."}
include_graphics("figure/zillow_middle_up.pdf")
```

```{r zillowmiddledown, fig.cap = "Rather than selecting mid-range series that recovered quickly, we can isolate those whose prices remained depressed after the recession. These seem mostly to be located in Central California and the East San Francisco Bay Area."}
include_graphics("figure/zillow_middle_down.pdf")
```

```{r zillowsf, fig.cap = "To study teh range in home prices within San Francisco County, we can select the associated nodes using a treebox."}
include_graphics("figure/zillow_sf.pdf")
```

@@

```{r working, fig.cap = "The two peaks at rush hour distinguish weekday series from the rest."}
include_graphics("figure/working.pdf")
```

```{r weekend, fig.cap = "Unlike weekday demand, weekend demand is unimodal. The few weekday series with unimodal series seem to be associated with holidays. This is the case for New Years' Eve, which is currently hovered over in the tree."}
include_graphics("figure/weekend.pdf")
```

```{r weekday2011, fig.cap = "Weeday demand appears larger in 2012 than 2011 -- compare with the next figure."}
include_graphics("figure/weekday_2011.pdf")
```

```{r weekday2012, fig.cap = "Weekday demand increased in 2012 -- compare with the previous figure."}
include_graphics("figure/weekday_2012.pdf")
```

```{r warmweekend, fig.cap = "The samples with highest night demand tend to fall on warm weekends."}
include_graphics("figure/warm_weekend.pdf")
```

```{r bikesankey, fig.cap = "We can interpret the regression tree using an interactive DOI representation."}
include_graphics("figure/bike_sankey.pdf")
```

@@

```{r iristimebox, fig.cap = "A toy application to the Iris data gives an example of how linking in treelapse can be applied to combine hierarchical clustering and parallel coordinates views."}
include_graphics("iris_timebox.pdf")
```

>>>>

We have implemented our visualizations in D3, but encapsulated in an R package,
called treelapse, to facilitate rapid turnover from data preparation and
modeling to interactive exploration, and vice versa. Our code is open-source,
and available at \url{https://github.com/krisrs1128/treelapse}. We hope this
package encourages data analysts to work at the border between data modeling and
visualization, and more generally empowers a wider audience to apply less widely
known, but powerful, visualization ideas.

@@

```{r antibioticoverview, fig.cap = "The two antibiotic time courses are readily apparent even when only highlighting the most abundant taxa."}
include_graphics("figure/antibiotic_overview.png")
```

```{r antibioticbacteroidetes, fig.cap = "Introducing a second box into the timebox display identifies the Bacteroidaceae as a taxon only midly impacted by antibiotics."}
include_graphics("figure/antibiotic_bacteroidetes.png")
```

@@

```{r ruminococcus, fig.cap = "By hovering over the Ruminoccocus branches, we see that there is a prolonged effect of the antibiotics time courses more or less uniformly across the lower taxonomic orders."}
include_graphics("figure/ruminococcus.png")
```

@@

```{r verrucomicrobiae, fig.cap = "The subtree averages aggregation brings attention to the Verrucomicrobiae, which though only present as a few species, are each rather abundant. In particular, they seem to increase after the first antibiotic time course."}
include_graphics("figure/verrucomicrobiae.png")
```

@@

```{r pretermcsts, fig.cap = "The increased diversity among samples in CST 4 is represented by the relatively larger contribution of red edges to branches outside of the Firmicutes."}
include_graphics("figure/preterm_csts.png")
```

```{r pretermcstslacto, fig.cap = "Zooming into the Lactobacillaceae family, we notice that the difference between the remaining four CSTs is related to which types of Lactobacillus are most prominent."}
include_graphics("figure/preterm_csts_lacto.png")
```

```{r pretermpreterm, fig.cap = "Samples with high levels of phyla other than Firmicutes appear to be related to preterm births."}
include_graphics("figure/preterm_preterm.png")
```

@@

```{r zillowcities, fig.cap = "California home prices at the city level, between 1996 and 2016. The effect of the 2008 recession is clear, and we have hovered over the San Bernardino series, to display the identity of one of the cities most strongly affected by the recession."}
include_graphics("figure/zillow_cities.png")
```

```{r zillowmiddlepre, fig.cap = "Neighborhoods with mid-range home prices before the recession are selected here. Note that the collection of series seems to widen after 2008 -- we are interested in whether there are reliable predictors of these alternate trajectories, given their similar starting points."}
include_graphics("figure/zillow_middle_pre.png")
```

```{r zillowmiddleup, fig.cap = "Among those neighborhoods with mid-range prices before the recession, we have selected those that recovered more rapidly. These appear to be located mainly in Los Angeles and San Diego counties."}
include_graphics("figure/zillow_middle_up.png")
```

```{r zillowmiddledown, fig.cap = "Rather than selecting mid-range series that recovered quickly, we can isolate those whose prices remained depressed after the recession. These seem mostly to be located in Central California and the East San Francisco Bay Area."}
include_graphics("figure/zillow_middle_down.png")
```

```{r zillowsf, fig.cap = "To study teh range in home prices within San Francisco County, we can select the associated nodes using a treebox."}
include_graphics("figure/zillow_sf.png")
```

@@

```{r working, fig.cap = "The two peaks at rush hour distinguish weekday series from the rest."}
include_graphics("figure/working.png")
```

```{r weekend, fig.cap = "Unlike weekday demand, weekend demand is unimodal. The few weekday series with unimodal series seem to be associated with holidays. This is the case for New Years' Eve, which is currently hovered over in the tree."}
include_graphics("figure/weekend.png")
```

```{r weekday2011, fig.cap = "Weeday demand appears larger in 2012 than 2011 -- compare with the next figure."}
include_graphics("figure/weekday_2011.png")
```

```{r weekday2012, fig.cap = "Weekday demand increased in 2012 -- compare with the previous figure."}
include_graphics("figure/weekday_2012.png")
```

```{r warmweekend, fig.cap = "The samples with highest night demand tend to fall on warm weekends."}
include_graphics("figure/warm_weekend.png")
```

```{r bikesankey, fig.cap = "We can interpret the regression tree using an interactive DOI representation."}
include_graphics("figure/bike_sankey.png")
```

@@

```{r iristimebox, fig.cap = "A toy application to the Iris data gives an example of how linking in treelapse can be applied to combine hierarchical clustering and parallel coordinates views."}
include_graphics("figure/iris_timebox.png")
```
